\Trill: Secure firewall-traversing networking

### 2012-11-12 6.858/proposal/proposal.tex
Header woo woo woo
Networking!

@@

\section*{Firewall Traversal}
Due to restrictions on many firewalls and NATs in place on the Internet, it is
impossible for arbitrary clients on the internet to establish peer-to-peer
communication. There are techniques for firewall/NAT traversal which involve
``tricking'' the networking layer into establishing a connection. We plan on
reimplementing something similar to \texttt{chownat} (http://samy.pl/chownat/),
which appears to be a standard way to do this.

\section*{Networking Abstractions}
% TODO

>>>>

\fancyhead[RO]{Carl Jackson and Max Wang}

@@

\section*{Firewall Traversal}
Due to restrictions on many firewalls and NATs in place on the Internet, it is
impossible for arbitrary clients on the internet to establish peer-to-peer
communication. There are techniques for firewall/NAT traversal which involve
``tricking'' the networking layer into establishing a connection. We plan on
reimplementing something similar to \texttt{chownat} (http://samy.pl/chownat/)
for \Trill, which appears to be a standard way to do this.

\section*{Networking Abstractions}
While using UDP allows us to traverse firewalls, it does not present a
particularly nice interface to the programmer. As always, those who do not
understand TCP are doomed to reimplement it, poorly. We hope to sidestep this
problem entirely by providing an abstraction more similar to SCTP: datagrams may
be of arbitrary length, and will arrive correctly ordered in their entirety or
not at all. However, datagrams may be received in any order relative to other
datagrams. We believe that this is the right level of abstraction to expose for
most peer-to-peer applications.

If time permits, we will additionally provide TCP-like congestion control in
\Trill.
